---
title: "Predicting Boston Housing Prices with Machine Learning"
author: "Timothy Pace"
date: "July 26, 2018"
output: github_document
---

## Preprocessing & EDA

```{r}
boston <- read.csv("Boston.csv")

boston <- boston[,c('nox', 'medv', 'dis', 'ptratio')]
plot(boston)
```

It appears that home value is tightly related to NO concentration, as well as distance to work and student to teacher ratio.

1) Fit single linear regressions with medv as the outcome and each of the predictors:

```{r}
mod1 <- lm(medv ~ nox, data = boston)
summary(mod1)

mod2 <- lm(medv ~ dis, data = boston)
summary(mod2)

mod3 <- lm(medv ~ ptratio, data = boston)
summary(mod3)
```


## What are the associations of NO, distance to employment, and education with home value?

Higher concentrations of NO are associated with decreased or lower home values (-33.92). For every NO increase by 1 part per million, home price goes down by about $34000. Greater distances to work are associated with increased or higher home values (1.09). For every increase by 1 kilometer in distance to work, home value goes up by about $1000. Lower ratios of teachers to students are associated with decreased or lower home values (-2.157). For every added student per teacher, home value decreases by about $2000.

## Which predictor explains the data the best?
Student to teacher ratio as a predictor of home values has the the highest adjusted r-squared value (0.26), and thus it explains the data the best.

## Runs a multiple linear regression with median housing price as the outcome and the other three variables as the predictors:

```{r}
mod.full <- lm(medv ~ dis + nox + ptratio, data = boston)
summary(mod.full)
```
	
### Interpretation

Surprisingly, by controlling for NO and student teacher ratio, home prices decrease the farther you live from work in Boston. In other words, when controling for air pollution and student to teacher ratio, greater distances to work are associated with lower home values. This may be because living closer to work is more convenient, and the price of this convenience is higher home values.

### Which model fits the data the best?

The adjusted r-squared value for the multivariate model is the highest at .40, and therefore fits the data best compared to all the single linear regression values (the highest of which is .26 for student to teacher ratio). Therefore, because the multivariate model explains the most variation in the data, it fits the data the best.


### Predicts and finds the prediction interval the median home value of a home 3 km from work, with a NO concentration of 0.35, and a student-teacher ratio of 10.

```{r}
predict(mod.full, newdata=data.frame("dis" = 3, "nox" = 0.35, "ptratio" = 10), interval="prediction")
```

The prediction interval of median home value when a home is 3 km from work, has a NO concentration of 0.35, and a student-teacher ratio of 10 is 49.57 (about $50000) with a lower bound of 35.23 (about $35000) and an upper bound of 63.92 (about $64000). 4